Storm surge modelling in the Strait of Georgia

### 2014-10-03 RoughWork/manuscript.tex
Moved tide table skeleton to an appendix
Modified description of tide-surge interaction

\begin{table}[h]
\centering 
\begin{tabular}{l l c c c c c c} 
\hline 
& & \multicolumn{3}{c}{M$_2$} & \multicolumn{3}{c}{K$_1$} \\ 
\hline 
Station number & Station name & $R$ & $ \Delta \phi$ (deg) & $D$ (cm) & $R$ & $ \Delta \phi$ (deg) & $D$ (cm) \\
\hline 
               &              &     &                      &          &     &                      &          \\
\hline   
Mean Error     &              &     &                      &          &     &                      &          \\
RMS Error      &              &     &                      &          &     &                      &          \\
\hline  
\end{tabular}
\caption{Comparisons of modelled and observed amplitudes and phases. $R$ is the ratio of modelled to observed amplitude. $\Delta \phi$ is the difference between modelled and observed phase. $D$ is the complex difference. }
\label{tab:comparison} 
\end{table}
%May have to include station numbers and locations on a map? Maybe on the contour map, overlay with stations and green/red dots (hopefully mostly green)
%Should we use the new method of calculating tides?

@@

Finally, an assessment of the importance of including the tide-surge interaction is presented next. A simulation of the surge propagation without including any tidal forcing is compared with the modelled residual in Figure \ref{fig:tidesurge}.  Recall, the modelled residual is defined as the difference between the sea surface height in a simulation with all forcing and a simulation with tides and rivers only. A comparison between the modelled residual and a surge-only run can determine the significance of the tide-surge interaction. The most significant differences occur at Point Atkinson where the maximum modelled residual is 7 cm lower than the maximum of the surge-only case.  In contrast, the tide-surge interaction at Victoria is hardly noticeable. Indeed, a spatial map of the modelled residual and surge-only difference (not shown here) indicates that the tide-surge interaction is more pronounced after the San Juan and Gulf Islands. The passages between these islands are known for vigorous tidal mixing, which may have an effect on the surge propagation. However, the effect is a relatively small underestimate of the surge elevation and no changes to the timing of the surge. So, in operational settings, performing a surge-only simulation and adding the predicted tides a posteriori could be more computationally efficient with only a small decrease in the accuracy of the prediction.

@@

>>>>

@@

Finally, an assessment of the importance of including the tide-surge interaction is presented next. A simulation of the surge propagation without including any tidal forcing is compared with the modelled residual in Figure \ref{fig:tidesurge}.  Recall, the modelled residual is defined as the difference between the sea surface height in a simulation with all forcing and a simulation with tides and rivers only. A comparison between the modelled residual and a surge-only run can determine the significance of the tide-surge interaction. The most significant differences occur at Point Atkinson where the maximum of the surge-only case is 8.6 cm higher than maximum modelled residual.  In contrast, the tide-surge interaction at Victoria is hardly noticeable. Indeed, a spatial map of the difference between the modelled residual and surge-only difference (not shown here) indicates that the tide-surge interaction is more pronounced after the San Juan and Gulf Islands. The passages between these islands are known for vigorous tidal mixing, which may have an effect on the surge propagation. However, the effect is a relatively small overestimate of the surge elevation and no changes to the timing of the surge. So, in operational settings, performing a surge-only simulation and adding the predicted tides a posteriori could be more computationally efficient with only a small decrease in the accuracy of the prediction.

@@

\section{Appendix}
\begin{table}[h]
\centering 
\begin{tabular}{l l c c c c c c} 
\hline 
& & \multicolumn{3}{c}{M$_2$} & \multicolumn{3}{c}{K$_1$} \\ 
\hline 
Station number & Station name & $R$ & $ \Delta \phi$ (deg) & $D$ (cm) & $R$ & $ \Delta \phi$ (deg) & $D$ (cm) \\
\hline 
               &              &     &                      &          &     &                      &          \\
\hline   
Mean Error     &              &     &                      &          &     &                      &          \\
RMS Error      &              &     &                      &          &     &                      &          \\
\hline  
\end{tabular}
\caption{Comparisons of modelled and observed amplitudes and phases. $R$ is the ratio of modelled to observed amplitude. $\Delta \phi$ is the difference between modelled and observed phase. $D$ is the complex difference. }
\label{tab:comparison} 
\end{table}
%May have to include station numbers and locations on a map? Maybe on the contour map, overlay with stations and green/red dots (hopefully mostly green)
%Should we use the new method of calculating tides?
